\section{Relevant Experience}

\parbox[t][][t]{\linewidth}{
    \parbox{\linewidth}{{\textbf{Junior Web Developer}}
        \hfill {{Jan. 2021 --- Present}}}
    \smallbreak
    
    \parbox{\linewidth}{stickee}
    \bigskip
}

\parbox[t][][t]{\linewidth}{
    \parbox{\linewidth}{{\textbf{Trainee Teacher of Computing}}
        \hfill {{Jan. 2020 --- Dec. 20}}}
    \smallbreak
    
    \parbox{\linewidth}{Arden Academy}
    
    \bigskip
    Placement teacher of OCR GCSE and A Level Computer Science at one of the top state schools in the UK.
    
    \bigskip
    \begin{itemize}
        \item{Planning, delivering, and reflecting upon lessons delivered to KS4 and KS5 students, incorporating strong subject knowledge and continuously improved pedagogical approach.}\\[-.6em]
        \item{Ensuring the needs of learners are met via differentiation and by developing inclusive learning resources.}\\[-.6em]
        \item{Marking work, tracking pupils' learning in order to prepare them for examination and further success on their learning journeys.}\\[-.6em]
        \item{Team teaching, observation, and directly assisting students with programming or technical work in classes not conducted by myself.}\\[-.6em]
    \end{itemize}
    \bigskip
}

\parbox[t][][t]{\linewidth}{
    \parbox{\linewidth}{{\textbf{Demonstrator (Teaching Assistant)}
        \hfill {{Sep. 2018 --- May. 19}}}}
    \parbox{\linewidth}{{Aberystwyth University
        \hfill {{Sep. 2017 --- May. 18}}}}
        \parbox{\linewidth}{{
            \hfill {{Sep. 2015 --- May. 16}}}}
    \smallbreak
    
    \bigskip
    Part-time teaching position for the Department of Computer Science. The role provides opportunities to reinforce technical and programming knowledge
    whilst also developing invaluable team-working and teaching skills.
            
    \bigskip
    \begin{itemize}
        \item{Demonstrating technical topics to undergraduate students to assist lecturing staff on the delivery of course content.}\\[-.6em]
        \item{Providing direct assistance to help students complete classroom based work and helping to instil good problem solving and computational thinking practices.}\\[-.6em]
        \item{Working together with other teaching staff and demonstrators to maximise support delivery across classes}\\[-.6em]
    \end{itemize}
    \bigskip
}

% \parbox[t][][t]{\linewidth}{
%     \parbox{\linewidth}{{\textbf{IT Support Specialist}}
%         \hfill {{Jul. 2017 --- May. 19}}}
%     \smallbreak
    
%     \parbox{\linewidth}{Nightline Association}
    
%     \bigskip
%     Volunteer position that I dedicate a substantial deal of time towards outside of work and study, in order to support the IT infrastructure of Nightline branches across the UK and Ireland, as well as the parent organisation, with the ongoing aim of reducing the occurrence of student suicide.
    
%     \bigskip
%     \begin{itemize}
%         \item{Writing user guides and documentation for both internal and external use, primarily on G-Suite and Confluence}\\[-.6em]
%         \item{Responding to queries made via email, JIRA Helpdesk, or Facebook}\\[-.6em]
%         \item{Helpdesk support for services provided to Nightlines and to the Association, including osTicket email, Google G-Suite, Mibew, WordPress, and our line of bespoke Laravel-based solutions}\\[-.6em]
%         \item{Work alongside a distributed agile team of support specialists and software engineers throughout the UK}\\[-.6em]
%         \bigskip
%         \bigskip
%     \end{itemize}
% }

\parbox[t][][t]{\linewidth}{
	\parbox{\linewidth}{{\textbf{Front-End Web Developer Intern}}
		\hfill {{Jul. 2016 --- Dec. 16}}}
	\smallbreak
    
	\parbox{\linewidth}{Amadeus IT Group}
    
	\bigskip
	Internship within Research \& Development of Amadeus Germany GmbH in Bad Homburg for my sandwich year in my undergraduate degree.
    
	\bigskip
	\begin{itemize}
		\item{Member of agile development team working on next-generation travel software solutions}\\[-.6em]
		\item{Using Confluence to document my work or to better understand software developed by my colleagues}\\[-.6em]
		\item{Prototyping front-end frameworks and web technologies, predominantly based on existing research}\\[-.6em]
		\item{Studying cutting edge technologies, including TypeScript and Redux, and partaking in programming seminars and learning opportunities}\\[-.6em]
		\item{Communicating predominantly in German language, both spoken and written}\\[-.6em]
	\end{itemize}
}
